% !TeX root = ../main.tex
% -*- coding: utf-8 -*-
% !TeX root = ../main.tex
% -*- coding: utf-8 -*-

\chapter*{个人简历}
\section*{\centerline{基本信息}}

作者徐思涵，女，1991年出生于江苏。

2009-2013 在南开大学 信息技术科学学院 攻读计算机科学与技术专业本科；

2016-2017 在新加坡国立大学 计算机学院 国家公派留学联合培养；

2013-2018 在南开大学 计算机学院 攻读计算机科学与技术专业博士。

\section*{\centerline{攻读博士学位期间发表论文}}

\begin{enumerate}[{[}1{]}]
	\item \textbf{Sihan Xu}, Sen Zhang, Weijing Wang, Xinya Cao, Chenkai Guo, Jing Xu. Method Name
	Suggestion with Hierarchical Attention Networks. The ACM SIGPLAN Workshop on Partial Evaluation
	and Program Manipulation (PEPM), 2019. (CCF-C, 已接收)
	\item \textbf{Sihan Xu}, Aishwarya Sivaraman, Siaucheng Khoo, Jing Xu. GEMS: An Extract Method Refactoring Recommender. The 28th International Symposium on Software Reliability Engineering (ISSRE), 2017. (CCF-B, Best paper runner-up)
	\item \textbf{Sihan Xu}, Chenkai Guo, Lei Liu and Jing Xu. A Log-linear Probabilistic Model for Prioritizing Extract Method Refactorings. The 3rd IEEE International Conference on Computer and Communications (ICCC), 2017. (EI)
	\item \textbf{Sihan Xu}, Jing Xu, Hongji Yang, Jufeng Yang, Chenkai Guo, Liying Yuan, Wenli Song, Guannan Si. An Improvement to Fault Localization Technique Based on Branch-Coverage Spectra. The 39th IEEE Annual International Computers, Software and Applications Conference (COMPSAC), 2015. (CCF-C)
	\item 文硕, 许静, 苑立英, \textbf{徐思涵}, 司冠南. 基于策略推导的访问控制漏洞测试用例生成方法[J]. 计算机学报, 2017, 40(12). (EI源刊)
	\item 过辰楷, 许静, 司冠南, 李恩鹏, \textbf{徐思涵}. 面向移动应用软件信息泄露的模型检测研究[J]. 计算机学报，2016, 39(11). (EI源刊)
	\item Chenkai Guo, Jing Xu, Lei Liu, \textbf{Sihan Xu}. MalDetector-using permission
	combinations to evaluate malicious features of Android App. The 6th IEEE International
	Conference on Software Engineering and Service Science (ICSESS), 2015. (EI)
	\item Chenkai Guo, Jing Xu, Lei Liu, \textbf{Sihan Xu}. Using association statistics to rank
	risk of android application, The IEEE International Conference on Computer and Communications
	(ICCC), 2016. (EI)
\end{enumerate}
